Assignment 4

### 2015-03-10 rmtw/a4/latex8.tex
fdsa
Added reason for Chi-Test

\SubSection{Test Used for H\textsubscript{fault}}
The frequency of A, B and C faults found were tabularised against the groups which found them. An example of this is found in table 3. In order to determine if they do find the same faults, a Chi-Square test of independence was performed on the tabulated results.

@@

>>>>

@@

\SubSection{Test Used for H\textsubscript{Fault}}
The frequency of A, B and C faults found were tabularised against the groups which found them. Any response that was not not applicable (NA) was discarded from the table. An example of this is found in table 3. In order to determine if they do find the same faults, a Chi-Square test of independence was performed on the tabulated results. The reason the Chi-Square test of independence was used was primarily because the data we wished to use were catagorical and the frequency of each category was at least 5. Other tests, such as Fishers Exact Test were not applicable, for example, our table was greater than 2x2 rows. Fishers test should only be used for 2x2 tables.
